Learning constraints in spreadsheets and tabular data

### 2016-12-19 Paper/ECAI/tabular.tex
WIP Autocompletion

\subsection{Effectiveness on real spreadsheets}
\added{
In order to test our approach on real data we assembled a benchmark of spreadsheets from three sources:
1)~spreadsheets from an exercise session for teaching Excel at the Brussels Business School based on the book~\cite{excel_book}, covering the most popular Excel formulas; 2)~spreadsheets from online tutorials on Excel formulas; and 3)~publicly available \textit{data} spreadsheets such as real-world crime statistics (FBI:UCR) or financial reports (US BEA). The data and its extended description are available in Appendix \ref{appendix:dataset_overview} in Table \ref{tab:constraint_by_category} and at the same repository\footref{github-link} with the links to all original publicly available spreadsheets used in the experiments (in the file \textit{links.txt}).
}

\sergey{Samuel, can you provide an extended technical description in github? Like straight in the README next to the tables?}

@@

\section{Applications}\label{sec:applications}
In this section, we illustrate how various applications can build on our method for solving the tabular constraint learning problem.

\subsection{Autocompletion}
Autocompletion can be seen as using knowledge derived from the current data to predict new values before they are written by the user.
A snapshot~($D_0$) is used to learn constraints and these are combined with new data~($\Delta D$) that the user has added.
Using~$\Delta D$ we can keep track of which vectors have changed and which vectors are now \textit{incomplete}.
\textit{Functional} constraints, such as $\ecsumc{\sbl{r}}{\mathbf{\sbl{x}}}$, are able to compute a result~($\sbl{r}$) based on its \textit{input}~($\mathbf{\sbl{x}}$).
If all vectors in the input blocks have changed and the result vector is incomplete, the constraint can compute the resulting value(s).

@@

\bibliographystyle{plain}
{
  \bibliography{references}}
\appendix
\section{Spreadsheet Dataset Overview}
\sergey{Samuel, we need an extended discussion here on how the data was obtained, I'll try a first sketch here}\\
There are three main sources for spreadsheets we have collected.
\begin{itemize}
  \item 
  \item 
  \item 
\end{itemize}

\begin{table}
  \centering
  \rowcolors{2}{gray!25}{white}
  \begin{tabular}{l | c c c }
    \textbf{Constraint} & \textbf{Exercises} & \textbf{Data} & \textbf{Tutorials}  \\\hline
    average (col) & 0 & 0 & 2 \\
    average (row) & 0 & 1 & 0 \\
    average-if & 1 & 0 & 0 \\
    count (col) & 0 & 0 & 1 \\
    count-if & 1 & 0 & 0 \\
    difference & 2 & 1 & 0 \\
    equal & 0 & 0 & 10 \\
    foreign-product & 1 & 0 & 0 \\
    fuzzy-lookup & 2 & 0 & 1 \\
    lookup & 1 & 0 & 0 \\
    max (col) & 0 & 0 & 2 \\
    max-if & 1 & 0 & 0 \\
    min (col) & 0 & 0 & 3 \\
    min-if & 1 & 0 & 0 \\
    percentual-diff & 5 & 1 & 0 \\
    product & 2 & 0 & 3 \\
    project & 1 & 0 & 0 \\
    rank & 1 & 0 & 0 \\
    series & 2 & 1 & 0 \\
    sum (col) & 5 & 0 & 10 \\
    sum (row) & 2 & 2 & 3 \\
    sum-if & 2 & 0 & 9 \\
    sum-product & 0 & 0 & 2 \\
  \end{tabular}
  \caption{Constraint occurrence by category}
  \label{tab:constraint_by_category}
\end{table}

\end{document}

>>>>

\subsection{Effectiveness on real spreadsheets}
\added{
In order to test our approach on real data we assembled a benchmark of spreadsheets from three sources:
  1)~spreadsheets from an exercise session for teaching Excel at the Brussels Business School based on the book~\cite{excel_book}, covering the most popular Excel formulas; 2)~spreadsheets from online tutorials on Excel formulas; and 3)~publicly available \textit{data} spreadsheets such as real-world crime statistics (FBI:UCR) or financial reports (US BEA). The data and its extended description are available at the same repository\footref{github-link} with the links to all original publicly available spreadsheets used in the experiments (in the file \textit{links.txt}).
}

\sergey{Samuel, can you provide an extended technical description in github? Like straight in the README?}

@@

\section{Applications}\label{sec:applications}
\added{In this section, we illustrate how two of the motivating applications, auto-completion and error checking, can build on our method for solving the tabular constraint learning problem.}

\subsection{Auto-completion}
Auto-completion can be seen as using knowledge derived from the current data to predict new values before they are written by the user.
\added{We can decompose this process into three phases: 1) learn constraints on a snapshot~($D_0$) of the spreadsheet, 2) new data~($\Delta D$) is added by the user, and 3) the system uses the learned constraints to predict missing values.
}
A snapshot~($D_0$) is used to learn constraints and these are combined with new data~($\Delta D$) that the user has added.
Using~$\Delta D$ we can keep track of which vectors have changed and which vectors are now \textit{incomplete}.
\textit{Functional} constraints, such as $\ecsumc{\sbl{r}}{\mathbf{\sbl{x}}}$, are able to compute a result~($\sbl{r}$) based on its \textit{input}~($\mathbf{\sbl{x}}$).
If all vectors in the input blocks have changed and the result vector is incomplete, the constraint can compute the resulting value(s).

@@

\bibliographystyle{plain}
{
  \bibliography{references}}
\end{document}
